Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
izing vs ising explanation of first approach

We only consider transfer function models, and require a $z$-domain
transfer function that captures all aspects of the continuous plant (with a
Laplace domain transfer function $G(s)$) and the sampling and hold process.
Note that $G(z)$ is a discrete model of a real-domain (and continuous)
plant, i.e., the continuous model of the plant must be discretised to obtain
the discrete equivalent coefficients via ZOH discretisation.

@@

\begin{myassumption}
%
The Sample and Hold of the ADC and the ZOH of the DAC are synchronized,
i.e., there is no delay between sampling the plant output at ADC and
updating the DAC accordingly.  The DAC interpolator is an ideal ZOH.
%
\end{myassumption}

\begin{mylemma}\cite{astrom1997computer}
%
Given a synchronized ZOH input and sample and hold output on the plant with
a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse
transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$
which can be computed using the following formula:
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = %\mathcal{ZOH}\left\lbrace{G(s)}\right\rbrace =
(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, we will use the notation $G(z)$ to represent the
pulse transfer function.
%
\end{mylemma}

@@

Given a model for a plant for which to synthesize a controller, provided in
an ANSI-C code input file (Steps 1-3), DSVerifier constructs a
non-deterministic model to represent the plant family (Step A), and
formulates a function (step B) using implementation details provided from
Step $2$ and $3$ to calculate the parameters of the controller to be
synthesized (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
controller synthesiser (Step D).

This intermediate ANSI-C code model contains a specification $\phi$ for the
verification properties ({\it i.e.}, robust stability) and is provided to
CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive
Synthesis (CEGIS) module, where the controller is marked as input variable
to synthesize.  The properties specified in the ANSI-C code model can only
be satisfied if CEGIS synthesizes controller coefficients satisfying $\phi$. 
CEGIS employs an iterative, counterexample-guided refinement process which
is explained in detail in section~\ref{synthesiser-general}.  A successful
synthesis result is reported if CEGIS generates a controller which is safe
with respect to $\phi$.  In particular, the ANSI-C code model guarantees
that a synthesized solution is complete and sound with respect to stability
property $\phi$, since it does not depend on system inputs and outputs.  In
the case of stability, the specification $\phi$ consists in a number of
assumptions on the polynomial coefficients, following Jury's Criteria, as
well as the restrictions set in the representation of these coefficients.

@@

There are two approaches for the {\sc verify} phase.
% based on the described model.  
The first approach uses interval arithmetic \cite{moore1966interval}
to represent the coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
and rounds operations outwards during calculations. 
%\cdsay{dario, what coefficients are these?}
% This results in a
% tighter calculation of the error at the cost of
% performance.
Synthesised controllers using this verifier will always
be correct and only generate counterexamples when the precision of the
engine is insufficient. Given the high computational cost of this
approach, we also designed a second approach, which we describe below.
Our experimental results described in Sec.~\ref{sec:experiments},  
%try both approaches and provide the time for the fastest. 
show that the increase in speed of the second approach 
over the first one is in most cases of several orders of magnitude.

@@

We have presented a CEGIS-based approach that uses inductive synthesis in
conjunction with an algorithm for verifying robust closed-loop stability, 
in order to compute a parametric solution for a digital controller given 
a continuous (or discrete) plant specification.  This enables us to automatically
synthesize correct-by-construction digital controllers for a given model of
their physical environment.  Our approach addresses the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  Our experimental results show that our CEGIS-based
approach is able to synthesise stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach to further
classes of systems.  We will also consider performance requirements while
synthesising the digital controller.

>>>>

We only consider transfer function models, and require a $z$-domain
transfer function $G(z)$ that captures all aspects of the continuous plant (with a
Laplace domain transfer function $G(s)$) and the sampling and hold process.
Note that $G(z)$ is a discrete model of a physical, continuous
plant, i.e., the continuous model of the plant must be discretised to obtain
the discrete equivalent coefficients via ZOH discretisation.

@@

\begin{myassumption}
%
The Sample and Hold of the ADC and the ZOH of the DAC are synchronised,
i.e., there is no delay between sampling the plant output at ADC and
updating the DAC accordingly.  The DAC interpolator is an ideal ZOH.
%
\end{myassumption}

\begin{mylemma}\cite{astrom1997computer}
%
Given a synchronised ZOH input and sample and hold output on the plant with
a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse
transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$
which can be computed using the following formula:
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = %\mathcal{ZOH}\left\lbrace{G(s)}\right\rbrace =
(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, we will use the notation $G(z)$ to represent the
pulse transfer function.
%
\end{mylemma}

@@

Given a model for a plant for which to synthesise a controller, provided in
an ANSI-C code input file (Steps 1-3), DSVerifier constructs a
non-deterministic model to represent the plant family (Step A), and
formulates a function (step B) using implementation details provided from
Step $2$ and $3$ to calculate the parameters of the controller to be
synthesised (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
controller synthesiser (Step D).

This intermediate ANSI-C code model contains a specification $\phi$ for the
verification properties ({\it i.e.}, robust stability) and is provided to
CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive
Synthesis (CEGIS) module, where the controller is marked as input variable
to synthesise.  The properties specified in the ANSI-C code model can only
be satisfied if CEGIS synthesises controller coefficients satisfying $\phi$. 
CEGIS employs an iterative, counterexample-guided refinement process which
is explained in detail in section~\ref{synthesiser-general}.  A successful
synthesis result is reported if CEGIS generates a controller which is safe
with respect to $\phi$.  In particular, the ANSI-C code model guarantees
that a synthesised solution is complete and sound with respect to stability
property $\phi$, since it does not depend on system inputs and outputs.  In
the case of stability, the specification $\phi$ consists in a number of
assumptions on the polynomial coefficients, following Jury's Criteria, as
well as the restrictions set in the representation of these coefficients.

@@

There are two approaches for the {\sc verify} phase.
% based on the described model.  
The first approach uses interval arithmetic \cite{moore1966interval}
to represent the coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
and rounds operations outwards during calculations. This effectively allows
us to simultaneously evaluate the whole collection of plants $\mathfrak{G}$
plus the effects of numeric calculations in the engine.
Synthesised controllers using this verifier will always
be stable for all plants in the family and only generate counterexamples when the precision of the
engine is insufficient (\emph{ie} no stable plant could be found). Given the high computational cost of this
approach, we also designed a second approach, which we describe below.
Our experimental results described in Sec.~\ref{sec:experiments},  
%try both approaches and provide the time for the fastest. 
show that the increase in speed of the second approach 
over the first one is in most cases of several orders of magnitude.

@@

We have presented a CEGIS-based approach that uses inductive synthesis in
conjunction with an algorithm for verifying robust closed-loop stability, 
in order to compute a parametric solution for a digital controller given 
a continuous (or discrete) plant specification.  This enables us to automatically
synthesise correct-by-construction digital controllers for a given model of
their physical environment.  Our approach addresses the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  Our experimental results show that our CEGIS-based
approach is able to synthesise stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach to further
classes of systems.  We will also consider performance requirements while
synthesising the digital controller.
